### 2016-10-25 paper/intro.tex

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption in the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been mostly
in parallelizing execution of tests using server farms,\Jbc{Is this an
assumption? Is there any evidence?} where worker machines from the
farm are assigned to execute distinct subsets of the original test
suite.

>>>>

Optimizing regression testing is important.  As software evolves test
sets become more complex (in number of tests or length of test runs),
potentially leading to disruption in the development process caused by
late reports of test failures. Several approaches have been
proposed in the literature to optimize regression testing.  Research
has focused mostly on test selection, test reduction, and test
prioritization~\Fix{cite cite...}.

Dealing with high testing costs is a common problem at large IT
companies (e.g., Groupon~\cite{kim-etal-fse2013}).  \Mar{Ask Milos if
  there is evidence on how prevalent regression testing is at
  Microsoft and Google, if he can explain how they run tests, and how
  prevalent is parallelization (in constrast to regression testing).}

\Fix{...decide how to motivate this study after results are shown.}

%% Although these approaches can also be
%% applied in industrial settings, the focus in industry has been mostly
%% in parallelizing execution of tests using server farms, where worker machines from the farm are
%% assigned to execute distinct subsets of the original test suite.
